A tool set for random number generation on GPUs in R

### 2022-01-12 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
stuff
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3110 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

int Drow, Dcol;
uint g1[3], g2[3];
int startvalue = (get_global_id(0) * get_global_size(1) + 
  get_global_id(1)) * NpadStreams;

const double fact[2] = { mrg31k3p_NORM_cl, TWOPI * mrg31k3p_NORM_cl };
const double addForSine[2] = { 0.0, - PI_2 };
local double part[2];

>>>>

int Drow, Dcol;
uint g1[3], g2[3];
int startvalue = (get_global_id(0) * get_global_size(1) + 
  get_global_id(1)) * NpadStreams;
const double fact[2] = { mrg31k3p_NORM_cl, TWOPI * mrg31k3p_NORM_cl };
const double addForSine[2] = { 0.0, - PI_2 };
local double part[2];
